---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BayesCPclust

<!-- badges: start -->
<!-- badges: end -->

BayesCPclust aims to estimate the change points in constant-wise data sequences while simultaneously performing clustering. A Gibbs sampler algorithm was developed to estimate the number of clusters, cluster assignments, number of change points, their positions, and constant levels.

## Installation

You can install the development version of BayesCPclust from [GitHub](https://github.com/) with:
      
``` r
# install.packages("devtools")
devtools::install_github("acarolcruz/BayesCPclust")
```

## Examples

To simulate constant-wise data sequences, you need to specify the variance of each data sequence and provide a list with a list for each cluster determining the following parameters (number of change points, their positions, and constant levels). The first argument in each list is the number of change points, then the positions for the change points, where $T_1 = 1, T_\text{last} = M + 1$, and for each interval between change points you need to specify a value for the constant level. 

```{r example1}
library(BayesCPclust)

# Simulating a dataset
set.seed(1238)
sigma2 <- round(extraDistr::rinvgamma(5, 21, 0.05*20),4)

param1 <- list(list(2, c(1, 19, 34, 51), c(5, 20, 10)), 
               list(2, c(1, 15, 32, 51), c(17, 10, 2)),
               sigma2)

data <- simdata(par.values = param1, d = 2, M = 50, w = 10, N = 5, as = 2,
                bs = 1000, emp = FALSE, seed = 1252)

```

The following example illustrate the process of performing clustering and estimations for constant-wise change-point data through a simulated scenario.

```{r example2}
# Running a simulation scenario with initial values
set.seed(1238)
sigma2 <- round(extraDistr::rinvgamma(5, 21, 0.05*20),4)

param1 <- list(list(2, c(1, 19, 34, 51), c(5, 20, 10)),
               list(2, c(1, 15, 32, 51), c(17, 10, 2)),
               sigma2)

initial_val <- list(c(param1[[1]][[1]], param1[[2]][[1]]),
                    list(c(1, 17, 32, 51), c(1, 13, 30, 51)),
                    list(c(6.5, 21.5, 11.5), c(18.5, 11.5, 3.5)),
                    round(extraDistr::rinvgamma(5, 21, 0.1*20),4))

sim_random(S = 1, seed = 1245, scenario = "TESTE", casenumber = 1,
           M = 50, N = 5, w = 10, d = 2, as = 2, bs = 1000, al = 2, bl = 1000,
           a = 2, b = 1000, alpha0 = 1/100, lambda = 2, maxIter = 50,
           startpoint_sampling = 2, par.values = param1, sigma2_equal = FALSE,
           emp = FALSE, initial_val = initial_val)
```


